Comparing tool variability and numerical variability in fMRI analyses

### 2021-12-02 paper/paper.tex
Update figures

@@

  %%%%%%%%%% plot different precisions%%%%%%%%
  \begin{figure}[ht]
    \fbox{\begin{minipage}{\dimexpr \columnwidth-2\fboxsep-2\fboxrule}
        \centering
        \includegraphics[width=\columnwidth]{figures/rmse-precisions.png}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
      \caption{Voxel-wise RMSE between BT and WT variability maps for different virtual precisions. \tristan{Remove (std) from y label}}
    \label{fig:across-precisions}
    \end{minipage}}
  \end{figure}

  %%%%%%%%%% plot different precisions%%%%%%%%
  \begin{figure}[ht]
    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
        \centering
        \includegraphics[width=\textwidth]{figures/bg_global_precision.pdf}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
        \caption{Unthresholded group t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).
        WT is computed at the virtual precision of t=17 bits. \tristan{remove (AFNI,SPM)}}
    \label{fig:gnp-mni}
    \end{minipage}}
  \end{figure}

@@

    % %%%%%%%%%% Dice plot of thresholded tstats%%%%%%%%
    \begin{figure*}[ht]
      \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
      \centering
      \includegraphics[width=\textwidth]{figures/dice_analysis-plot.png}
      \caption{Confusion matrices of activation instability
      in BT and WT among the 360 regions from the HCP-MMP1.0 parcellation. \tristan{plot a single color map for 3 heatmaps}}
      \label{fig:cm-thresh}
    \end{minipage}}
    \end{figure*}

>>>>

\begin{figure*}[ht]
  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
    \begin{subfigure}[ht]{\textwidth}
      \centering
      \includegraphics[width=.6\textwidth]{figures/sbj-std-corr-unthresh-plot.png}
      %\caption{Standard deviation of thresholded t-statistics map on template surface}
    \end{subfigure}
    \caption{
      Voxel-wise comparison of BT and WT variabilty subject by subject.}
  \label{fig:unthresh-correlation-allsbj}
  \end{minipage}}
\end{figure*}

@@

  %%%%%%%%%% plot different precisions%%%%%%%%
  \begin{figure}[ht]
    \fbox{\begin{minipage}{\dimexpr \columnwidth-2\fboxsep-2\fboxrule}
        \centering
        \includegraphics[width=\columnwidth]{figures/rmse-precisions.png}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
      \caption{Voxel-wise RMSE between BT and WT variability maps for different virtual precisions.}
    \label{fig:across-precisions}
    \end{minipage}}
  \end{figure}

  %%%%%%%%%% plot different precisions%%%%%%%%
  \begin{figure}[ht]
    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
        \centering
        \includegraphics[width=.75\textwidth]{figures/bg_global_precision.pdf}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
        \caption{Unthresholded group t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).
        WT is computed at the virtual precision of t=17 bits.}
    \label{fig:gnp-mni}
    \end{minipage}}
  \end{figure}

  \begin{figure*}[ht]
    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
      \begin{subfigure}[ht]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/std-corr-unthresh-vp17-plot.png}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
      \end{subfigure}
      \caption{
        Voxel-wise comparison of BT and WT variabilty. WT is computed with FSL at the virtual precision of t=17 bits.}
    \label{fig:unthresh-correlation-gvp}
    \end{minipage}}
  \end{figure*}

@@

    % %%%%%%%%%% Dice plot of thresholded tstats%%%%%%%%
    \begin{figure*}[ht]
      \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
      \centering
      \includegraphics[width=\textwidth]{figures/dice_analysis-plot.png}
      \caption{Confusion matrices of activation instability
      in BT and WT among the 360 regions from the HCP-MMP1.0 parcellation.}
      \label{fig:cm-thresh}
    \end{minipage}}
    \end{figure*}
